%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Relevant Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer Fellow, Web Development Track} % Job title
    {CUNY Tech Prep} % Organization
    {New York, NY} % Location
    {Jun. 2020 - May. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Selected for a year-long technical training program to learn web development and gain industry exposure to software development and a connection to tech jobs post-graduation.}
        \item {Learned in-demand technologies like React, Node + Express, and PostgreSQL, as well as industry best practices for design and implementation.}
        \item {Understood deployment such as MVC, version control with Git/GitHub, Agile \& Scrum with Trello and Slack, test driven development, and CI/CD.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CodeLabs Intern, Advanced Track} % Job title
    {CodeDay} % Organization
    {USA} % Location
    {Jul. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated virtually with two other CodeLabs interns throughout the country to create a Discord bot that returns stories from Hacker News based on user-commands.}
        \item {Learned and utilized the discord.py library to connect the Discord bot with Hacker News by using the Hacker News API and filtering stories based on the user preferences using a list of common technological terms.}
        \item {Implemented CI/CD using GitHub Actions and Heroku for automated building, testing, and deploying, which takes around 1 minute to complete every time a pull request is merged.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
