%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Technologies: React.js, HTML, CSS, Material-UI, JavaScript, Node.js, Express.js, Sequelize, PostgreSQL, Git/GitHub, Heroku, Figma.} % Technologies
    {\href{https://simplemta.herokuapp.com/}{SimpleMTA}} % Project Name
    {} % Location
    {Mar. 2021 - May. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Worked in a team of three to create a more simple version of NYC's MTA website by providing users with an easy way to look up train lines and train stations and an easy way to bookmark stations.}
        \item {Implemented responsive, mobile-first Login, Register, and Home Page components using React.js, React Hooks, and Material-UI.}
        \item {Wireframed initial design using Figma, implemented final design using React.js, and then deployed using Heroku.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Technologies: React.js, HTML, CSS, JavaScript, Node.js, Express.js, MongoDB, Git/GitHub.}
    {\href{https://github.com/opensource-ny/OpenSource-NY}{OSNY (Open Source New York) App}}
    {}
    {Feb. 2019 - Dec. 2019}
    {
      \begin{cvitems}
        \item {Collaborated on an open-source web application to track user PRs in GitHub repositories.}
        \item {Built the user interface and user experience using HTML and CSS in React.js, which created a clear and concise website.}
        \item {Reviewed PRs and added documentation to ensure there were no problems for new features in the app on GitHub.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
